### 2021-09-01 presentation/presentation.tex
change color
use includegraphics
add short url
update presentation

% This file is a solution template for:

% - Talk at a conference/colloquium.
% - Talk length is about 20min.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

@@

  \setbeamercolor{palette primary}{bg=red!50!black!80}
  \setbeamercolor{palette secondary}{bg=red!50!black!70}
  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
  \setbeamercolor{palette quaternary}{bg=gray!90!black!100}

@@

  % \setbeamercolor{author in head/foot}{bg=grey!60}
  \setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}
\makeatletter
\setbeamertemplate{page number in head/foot}[appendixframenumber]
\setbeamertemplate{headline}
{%
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \centering
    \usebeamerfont{author in head/foot}\insertsection{}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
    \centering
    \insertsubsection{}
  \end{beamercolorbox}%
  }%
  \vskip0pt%
}
\setbeamertemplate{footline}
{%
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}%
    \centering
    \usebeamerfont{date in head/foot}\usebeamercolor[fg]{page number in head/foot}\usebeamerfont{page number in head/foot}\usebeamertemplate{page number in head/foot}
    % \hspace*{2ex}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \centering
    \usebeamerfont{author in head/foot}\insertshortauthor{}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.65\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
    \centering
    \insertshorttitle{}
  \end{beamercolorbox}%
  }%
  \vskip0pt%
}
\makeatother

@@

@@

\date[SysTol'21] % (optional, should be abbreviation of conference name)
{5th International Conference on Control and Fault-Tolerant Systems, 2021
                      \includegraphics[width=2cm]{../img/qrPresentation.png}
}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\subject{}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

\pgfdeclareimage[height=.8cm]{university-logo}{../img/logos/supelec.jpeg}
\logo{\pgfuseimage{university-logo}}

@@

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

@@

\begin{frame}[plain]
  \titlepage
\end{frame}

@@

    % The following outlook is optional.
    \vskip0pt plus.5fill
    \begin{itemize}
      \item
            Outlook
            \begin{itemize}
              \item
                    Inequality Constraints yield Hybrid behavior
              \item
                    Non-linear attack model
            \end{itemize}
      \item Repository
\vspace{-.4cm}

                    \begin{minipage}{.6\textwidth}
                      \url{https://github.com/Accacio/SysTol-21}
                    \end{minipage}
                    \begin{minipage}{.2\textwidth}
                      \includegraphics[width=2cm]{../img/qrRepo.png}
                    \end{minipage}
    \end{itemize}
  \end{minipage}
\end{frame}

\nocite{VelardeEtAl2017a}
% All of the following is optional and typically not needed.
\appendix
\section<presentation>*{\appendixname}
\subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
\bibliographystyle{IEEEtran}
\bibliography{../article/bibliography}
  \frametitle<presentation>{For Further Reading}

@@

  \beamertemplatebookbibitems
  % Start with overview books.
\bibitem{MaestreEtAl2014}
J.~M. Maestre, R.~R. Negenborn \emph{et~al.}, \emph{{D}istributed {M}odel
  {P}redictive {C}ontrol made easy}.\hskip 1em plus 0.5em minus 0.4em\relax
  Springer, 2014, vol.~69.

  \bibitem{Author1990}
    A.~Author.
    \newblock {\em Handbook of Everything}.
    \newblock Some Press, 1990.

@@

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}

>>>>

@@

  \setbeamercolor{palette primary}{bg=red!50!black!80}
  \setbeamercolor{palette secondary}{bg=red!50!black!70}
  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
  \setbeamercolor{palette quaternary}{bg=gray!90!black!70}
  \setbeamercolor{block title}{bg=red!50!black!70}

@@

  \setbeamercolor{bibliography entry author}{fg=red!50!black!80}
  \setbeamercolor{bibliography entry location}{fg=red!50!black!40}

  % \setbeamercolor{author in head/foot}{bg=grey!60}
  \setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}
\makeatletter
\protected\def\protectedempty{}
\setbeamertemplate{page number in head/foot}[appendixframenumber]
\setbeamertemplate{footline}
{%
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}%
    \centering
    \usebeamerfont{date in head/foot}\usebeamercolor[fg]{page number in head/foot}\usebeamerfont{page number in head/foot}\usebeamertemplate{page number in head/foot}
    % \hspace*{2ex}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \centering
    \usebeamerfont{author in head/foot}\insertshortauthor{}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.65\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
    \centering
    \insertshorttitle{}
  \end{beamercolorbox}%
  }%
  \vskip0pt%
}
\makeatother

\setbeamertemplate{sidebar right}{
  \vfill%
  \llap{\insertlogo\hskip0.2cm}%
  \vskip3pt%
  \llap{\usebeamertemplate***{navigation symbols}\hskip0.1cm}%
  \vskip2pt%
}
\setbeamertemplate{headline}
{%
  \leavevmode%
  \hbox{%
      \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,center]{section in head/foot}%
      \centering
      \usebeamerfont{author in head/foot}\insertsection{}
    \end{beamercolorbox}%
  % }
    \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,right]{subsection in head/foot}%
      \centering
      \insertsubsection{}
    \end{beamercolorbox}%
    }
  \vskip0pt%
}

@@

\usepackage{bm}
\usepackage[ruled,noend]{algorithm2e}
\SetKwRepeat{Do}{do}{while}

\newcommand{\eq}[2]{\mbox{$#1=#2$}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Np}{N_{\text{p}}}
\newcommand{\T}{^{\mathrm{T}}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\0}{\mathbf{0}}
\newcommand{\abs}[1]{\left\lvert#1\right\rvert}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\Varepsilon}{\mathcal{E}}
\newcommand{\diff}{\mathop{}\mathopen{}\mathrm{d}}
\newcommand{\set}[1]{\mathcal{#1}}
\newcommand{\p}{^{(p)}}
\newcommand{\pplusone}{^{(p+1)}}
\renewcommand{\vec}[1]{\bm{#1}}
\newcommand{\enstq}[2]{\{#1\mathrel{}\mid\mathrel{}#2\}}

@@

\date[SysTol'21] % (optional, should be abbreviation of conference name)
{5th International Conference on Control and Fault-Tolerant Systems, 2021
  \begin{minipage}{.3\textwidth}
    \centering
    \includegraphics[width=2cm]{../img/logos/logo_IETR.png}
  \end{minipage}
  \begin{minipage}{.3\textwidth}
    \centering
    \vspace{10pt}
    \includegraphics[width=1.5cm]{../img/qrPresentation.png}
    \href{https://git.io/JEFGW}{https://git.io/JEFGW}
  \end{minipage}
  \begin{minipage}{.3\textwidth}
    \centering
    \vspace{10pt}
    \includegraphics[width=2cm]{../img/logos/supelec.jpeg}
  \end{minipage}
}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\subject{}

\logo{\includegraphics[height=.8cm]{../img/logos/supelec.jpeg}}

@@

@@

\begin{frame}[plain]
  \titlepage%
\end{frame}

% \begin{frame}[fragile]
% \frametitle{An Algorithm For Finding Primes Numbers.}
% \begin{semiverbatim}
% \uncover<1->{\alert<0>{int main (void)}}
% \uncover<1->{\alert<0>{\{}}
% \uncover<1->{\alert<1>{ \alert<4>{std::}vector<bool> is_prime (100, true);}}
% \uncover<1->{\alert<1>{ for (int i = 2; i < 100; i++)}}
% \uncover<2->{\alert<2>{
% if (is_prime[i])}}
% \uncover<2->{\alert<0>{
% \{}}
% \uncover<3->{\alert<3>{
% \alert<4>{std::}cout << i << " ";}}
% \uncover<3->{\alert<3>{
% for (int j = i; j < 100;}}
% \uncover<3->{\alert<3>{
% is_prime [j] = false, j+=i);}}
% \uncover<2->{\alert<0>{
% \}}}
% \uncover<1->{\alert<0>{ return 0;}}
% \uncover<1->{\alert<0>{\}}}
% \end{semiverbatim}
% \visible<4->{Note the use of \alert{\texttt{std::}}.}
% \end{frame}

\begin{frame}
\SetKwBlock{negotPhase}{ Negotiation Phase:}{}
\SetKwBlock{detectPhase}{ Detection Phase:}{}
\scalebox{.8}{  \begin{algorithm}[H]
    \DontPrintSemicolon
    \detectPhase{
    $h:=0$\;
    \Repeat{
    $\|\eta_{i}^{h}-\eta^{h-1}\|\leq\epsilon$
  }{
    Coordinator sets random $\vec{\theta}_{i}^{(h+1)}$ \;
    Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}^{(h)})$\;
    Coordinator estimates $\widehat{\tilde{P}}_{i}(k)^{(h)}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)^{(h)}$ \;
    $h:=h+1$\;
  }
    Coordinator computes $d_{i}$ using~\eqref{eq:2}\;
  }
    \negotPhase{
    Coordinator initializes $\vec{\theta}^{(0)}$ \;
    $p:=0$\;

    \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
    Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;

    Coordinator updates allocation~\eqref{eq:thetaNegot} using adequate versions of $\vec{\lambda}_{i}$ for each agent: $\vec{\lambda}_{i}^{\star}(\vec{\theta}\p)$, if $d_{i}=0$ and ${\vec{\lambda}_{i}}_{\mathrm{rec}}$, if ${d_{i}=1}$\;
    $p:=p+1$
  }}
    \caption{Secure DMPC.}\label{alg:safeDMPC}
  \end{algorithm}
  }
\end{frame}

\begin{frame}
  \centering
  \begin{minipage}{.65\linewidth}
    \begin{algorithm}[H]
      \DontPrintSemicolon
      Coordinator initializes $\vec{\theta}^{(0)}$ \;
      $p:=0$\;
      \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
        Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
        Coordinator updates allocations~\eqref{eq:thetaNegot}\;
        $p:=p+1$
      }
      \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
    \end{algorithm}
  \end{minipage}
\end{frame}

@@

    % The following outlook is optional.
    \vskip0pt plus.5fill
    \begin{itemize}
      \item
            Outlook
            \begin{itemize}
              \item
                    Inequality Constraints yield Hybrid behavior
              \item
                    Non-linear attack model
            \end{itemize}
    \end{itemize}
  \end{minipage}
\end{frame}

\nocite{VelardeEtAl2017a}
% All of the following is optional and typically not needed.
% \appendix
% \section<presentation>*{\appendixname}
% \subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
% \bibliographystyle{IEEEtran}
% \bibliography{../article/bibliography}
  \frametitle<presentation>{For Further Reading}

@@

  \beamertemplatebookbibitems
  % Start with overview books.
  \bibitem{MaestreEtAl2014}
  J.~M. Maestre, R.~R. Negenborn \emph{et~al.}
  \newblock \emph{{D}istributed {M}odel {P}redictive {C}ontrol made easy}.\hskip 1em plus 0.5em minus 0.4em\relax
  \newblock Springer, 2014, vol.~69.

@@

\bibitem{VelardeEtAl2017a}
P.~Velarde, J.~M. Maestre, H.~Ishii, and R.~R. Negenborn,
\newblock ``Scenario-based
defense mechanism for distributed model predictive control,''
\newblock \emph{2017
  IEEE 56th Annual Conference on Decision and Control (CDC)}.\hskip 1em plus
  0.5em minus 0.4em\relax IEEE, Dec 2017, pp. 6171--6176.

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}
\begin{frame}[plain]
  \centering
  \vfill
       Questions?
\vfill
\begin{minipage}[t]{.45\linewidth}
  \centering
  Repository

  \href{https://github.com/Accacio/SysTol-21}{https://github.com/Accacio/SysTol-21}

  \includegraphics[width=2cm]{../img/qrRepo.png}
\end{minipage}
\begin{minipage}[t]{.5\linewidth}
  \centering
  Contact
  \href{mailto:rafael-accacio.nogueira@centralesupelec.fr?subject=SysTol'21 Presentation}{rafael-accacio.nogueira@centralesupelec.fr}

    \includegraphics[width=2cm]{../img/qrContact.png}
\end{minipage}
\end{frame}
